Wolbachia, Toxoplasma and O. Cordyceps: Extreme Host-Manipulating Microbes That Are Changing the World

### 2015-12-17 paper.tex
Fixes

\textit{Toxoplasma gondii} is a microbe that we may have only discovered 107 years ago, and most people have never heard of it, but it still has a large impact on the human population. ``Infection with \textit{Toxoplasma gondii} can cause severe illness when the organism is contracted congenitally or when it is reactivated in immune-suppressed persons” \cite{Tsero}, which is how it most greatly affects people. Many people afflicted by AIDS or cancer have developed toxoplasmosis due to the weakened state of their immune systems. Children are also at risk for serious complications caused by \textit{T. gondii}, as exemplified by the fact that when research into this microbe began, one of the first examined victims was an infant girl who died at one month old due to congenital toxoplasmosis \cite{Tlife_cycle}.

@@

Let’s not forget that \textit{Toxoplasma gondii} is found everywhere. Birds carry it and can shed the oocysts, spreading the microbe \cite{Tbirds}. There is speculation that dogs might carry it on their fur and aid in the transmission of the microbe to humans \cite{Tdogs}. And scientists have come to believe that ``some 25 percent of the global human population is chronically infected with T. gondii” \cite{TUSDA}. Currently, there is no vaccine that is safe for humans to use against \textit{T. gondii} \cite{Tvaccine}, but research is continuing, particularly at the Toxoplasmosis Research Institute and Center in Chicago, IL. This microbe may have bigger plans for us than we can even imagine at this point, so research into it should continue until we understand it better.

>>>>

\textit{Toxoplasma gondii} is a microbe that we may have only discovered 107 years ago, and most people have never heard of it, but it still has a large impact on the human population. ``Infection with \textit{Toxoplasma gondii} can cause severe illness when the organism is contracted congenitally or when it is reactivated in immune-suppressed persons"\cite{Tsero}, which is how it most greatly affects people. Many people afflicted by AIDS or cancer have developed toxoplasmosis due to the weakened state of their immune systems. Children are also at risk for serious complications caused by \textit{T. gondii}, as exemplified by the fact that when research into this microbe began, one of the first examined victims was an infant girl who died at one month old due to congenital toxoplasmosis \cite{Tlife_cycle}.

@@

Let’s not forget that \textit{Toxoplasma gondii} is found everywhere. Birds carry it and can shed the oocysts, spreading the microbe \cite{Tbirds}. There is speculation that dogs might carry it on their fur and aid in the transmission of the microbe to humans \cite{Tdogs}. And scientists have come to believe that ``some 25 percent of the global human population is chronically infected with T. gondii" \cite{TUSDA}. Currently, there is no vaccine that is safe for humans to use against \textit{T. gondii} \cite{Tvaccine}, but research is continuing, particularly at the Toxoplasmosis Research Institute and Center in Chicago, IL. This microbe may have bigger plans for us than we can even imagine at this point, so research into it should continue until we understand it better.
